Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2014-12-29 wearables_survey.tex
methodology un-roughed (except riskandben section)

\section{Methodology}
The survey consisted of questions regarding concerns with respect to a factious wearable device called the Cubetastic3000 (this was done to prevent any biases in answers from participants with respect to specific companies), smartphone concerns, risk and benefit assessment of technologies, and exit questions. Details on the question ordering, question formatting, and sample questions are below. The full survey can be found at http://www.surveygizmo.com/s3/1657924 /Wearables-Threats-User-Survey.

(REDO) In total, the survey consisted of 367 unique questions, with each participant answering 27 questions. Out of the 27 seen by the participant, 10 of the questions are randomly selected from a particular set of questions (see below).   \\[-.8cm]

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item 2 comprehension questions 
\item 6/305 questions about various scenarios 
\item 2/5 questions about smartphone scenarios 
\item 1/20 benefit questions 
\item 1/20 risk questions (same technology) 
\item 4 demographics
\item 1 open-ended question 
\item 10 questions of IUIPC \\[-.8cm]
\end{itemize}

To mitigate any biases, we randomized the order in which users saw groups of questions. That is; the participant has an equal chance of seeing questions related to threat perceptions or questions related to risk and benefit assessment of technologies. Additionally, each question in the sections about various scenarios, questions about smartphone scenarios, and IUIPC questions were randomly selected. A participant was also equally likely to see the risk or benefit questions first when they got to the section pertaining to risk and benefit assessment of technologies.

\subsection{Comprehension Questions}
Before they get to the wearable device question, they must answer these two questions about the Cubetastic3000. people who did not answer these two comprehension questions were filtered out (this was about 4\% of our participants)

\textit{Where and when would you wear the Cubetastic3000?}\\[-.5cm]

\textit{What can the Cubetastic3000 do?}

\subsection{Scenarios}

The purpose of the 6/305 questions were to determine how much the device, data type, and data recipient played a role in determining if a person was upset by an event or not. These are word for word modeled after the mobile user study. You can see that in the first example question, these three controls are highlighted. Other questions were used for calibration with the smartphone study, where we literally ask the same questions as the study, but toggling the device type, to see if this plays a role in risk perception.

\textit{How would you feel if an app on your Cubetastic3000 learned how you were feeling based on your heart rate and shared that with the public, without asking you first}\\[-.5cm]

\textit{How would you feel if an app on your smartphone connected to a Bluetooth device (like a headset) without asking you first?}

\subsection{Smartphone}
Calibration ones

\subsection{Risk and Benefit}
The next set of questions are with respect to the Fischoff study on users’ perception of benefit and risk. We wanted to study personal but also broad perceptions of wearble risks. the We prompted the users with the same prompt that the participants in the Fischoff study was presented with, giving instructions to consider gross risk and gross benefits for a long period of time for all people, with specific instructions to numerical rankings. We did this so that we can calibrate the new technologies that we ask about with the existing seminal study. Prompt can be seen at appendix \ref{sec:prompt}.

@@

\subsection{Additional Questions}
(REDO) During the exit portion of the survey, we asked for demographics (gender, age, education), if the person owns a wearable or not, and the IUIPC index. Explain why I used IUIPC instead of the Westin, just one or two sentences will do (cite the IUPIC paper, and the SOUPS paper on how the Westin is not so accurate).

\textit{What do you think are the most likely risks associated with wearable devices?}

\subsection{Focus Group}
We conducted a focus group to validate our survey scope. Of the 13 participants 54\% female, ages ranged from 18 to 64 (mu = 36.1, sigma = 15.3).  Education backgrounds ranged from high school to doctorate degrees, and professions included student, artist, marketer, and court psychologist. This time was used to discuss benefits and risks associated with wearables, talk through common concerns, and brainstorm additional scenarios for the survey. The focus group was also used to gauge survey comprehension, user fatigue, and other logistics.

@@

>>>>

\section{Methodology}
The survey consisted of questions regarding concerns with respect to a factious wearable device called the Cubetastic3000 (done to prevent biases in answers from participants with respect to specific artifacts or companies), smartphone concerns, risk and benefit assessment of technologies, and exit questions. Details on the question ordering, question formatting, and sample questions are below. The full survey can be found at http://www.surveygizmo.com/s3/1657924 /Wearables-Threats-User-Survey.

In total, the survey consisted of 367 unique questions, with each participant answering 27 questions. Out of the 27 seen by each participant, 17 of the questions were constant, whereas 10 of the questions were selected at random from larger sets of questions. During the course of the survey, each participant answered:   \\[-.8cm]

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item 2 comprehension questions 
\item 6/304 questions about various wearables scenarios 
\item 2/5 questions about smartphone scenarios 
\item 1/20 benefit questions 
\item 1/20 risk questions (same technology) 
\item 4 demographics
\item 1 open-ended question 
\item 10 questions of IUIPC \\[-.8cm]
\end{itemize}

To mitigate any biases, the order in which question groups appeared to the user was randomized. Specifically, a participant had an equal chance of seeing questions related to the Cubetastic3000 or questions related to risk and benefit assessment. When a participant saw the risk and benefit assessment questions, risk or benefit questions were equally likely to be shown first. Whenever applicable, questions were randomly selected. For risk and benefit assessment, a technology was randomly selected for each participant, then risk and benefit questions for the same technology were selected for the participant.

\subsection{Comprehension Questions}
Because we were asking questions about a fictitious device, participants were presented with two comprehension questions before the start of the wearable device scenarios questions. These questions served to ensure that participants would be informed of the device which we were going to be referring to, but also served as a filter for people who were inattentive or chose not to answer questions correctly. Filtering incomplete and incorrect responses to either of these comprehension questions filtered out 16\% (n = 366) of our participants, which were 79\% of all incomplete or bad responses (n = 464).

\subsection{Wearables Scenarios}
%okay, this section is kind of confusing, I must admit..

After participants had answered the two comprehension questions, participants were presented with 6 randomly selected questions from a set of 304 questions on various scenarios which can occur when wearing the Cubetastic3000 fictitious wearable device. Out of these 304 questions, 292 (73 data * 4 recipients) were questions of the format: \textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}. Additionally, there were 13 questions which did not follow the above format, lacking data to be shared and/or a recipient of any data. Of these questions, 5 questions were to calibrate with Felt's study on smartphones and the other 7  were exploratory questions. An example of a regular question, a calibration question, and exploratory question, respectively, are below:

\textit{How would you feel if an app on your Cubetastic3000 learned how you were feeling based on your heart rate and shared that with the public, without asking you first?}\\[-.5cm]

\textit{How would you feel if an app on your Cubetastic3000 connected to a Bluetooth device (like a headset) without asking you first?} \\[-.5cm]

\textit{How would you feel if an app on your Cubetastic3000 turned your device off, without asking you first?}\\[-.5cm]

The main purposes of these questions were to, firstly, determine how much the device, data type, and data recipient played a role in determining if a person was upset by an event or not and, secondly, to investigate what information would most upset users when shared and which recipient of the shared data would most upset users. The calibration questions were modeled after Felt's mobile user study, where we ask the same questions but with respect to wearables rather than smart phones, to see if a change in device changes users' risk perception. The remaining exploratory questions were additional scenarios which did not fit the standard question format but were relevant to ask our participants.

\subsection{Smartphone Scenarios}
Following the wearables scenario questions were 2 randomly selected questions from a set of 5 questions on various scenarios which can occur when using a smartphone. These five scenarios, ranging from the most upsetting scenario to the least upsetting scenario, were purposefully selected from Felt's mobile user study for eliciting varying reactions from users. These questions were the basis for the five calibration wearables scenarios from the above section. Because we asked users questions differing only by the device in question, we are able to see how the change in device changes users' risk perception. Additionally, we compare our participants' perceptions of wearable device scenarios with existing perceptions of mobile device scenarios.

\subsection{Risk and Benefit Assessment}
The next set of questions are with respect to the Fischoff study on users’ perception of benefit and risk. We wanted to study personal but also broad perceptions of wearble risks. the We prompted the users with the same prompt that the participants in the Fischoff study was presented with, giving instructions to consider gross risk and gross benefits for a long period of time for all people, with specific instructions to numerical rankings. We did this so that we can calibrate the new technologies that we ask about with the existing seminal study. Prompt can be seen at appendix \ref{sec:prompt}.

@@

\subsection{Additional Questions}
The exit portion of the survey consisted of demographics questions to better understand the answers. We included standard demographics questions such as age, gender, and education status, but also asked participants if they owned a wearable device to survey the population's exposure to these devices, prompted them with an open-ended question on what would be the most likely risks associated with wearable devices, and finished with questions from a privacy index to gauge their privacy preferences. We used the Internet Users' Information Privacy Concerns (IUIPC) index \cite{malhotra2004internet}, rather than the Westin Index, which was found to be very coarse \cite{woodruff2014would}.

\subsection{Focus Group}
We conducted a one-hour focus group to validate our design, gauge survey comprehension, and measure user fatigue. The focus group began with participants taking the survey. Afterward, the participants were asked to give feedback on the format and the content of the survey, noting any instructions or questions which were unclear and stating any suggestions for the content of the survey. The focus group concluded with a discussion of possible benefits and risks of wearable devices, to brainstorm any additional scenarios which may occur. Afterward, participants were debriefed and given \$30 in cash. Of the 13 participants 54\% female, ages ranged from 18 to 64 (mu = 36.1, sigma = 15.3).  Education backgrounds ranged from high school to doctorate degrees, and professions included student, artist, marketer, and court psychologist.

@@

Specifically, people are most upset about x, y, z, when shared with public, work, or friends.

People have different expectations of privacy when they perceive that data is being shared with an app rather than a human audience.
